### 2023-05-01 chapter2/chapter2.tex
Fixed wrong citation for Felsenstein contrasts

\subsection{Brownian motion and Ornstein-Uhlenbeck analyses}
Brownian motion (BM) model parameters were calculated with two methods. The first used Felsenstein's contrasts algorithm to efficiently calculate roots and contrasts for the disorder scores and features of each region~\cite{Felsenstein1973, Felsenstein1981}. Rates were calculated as the mean of the squares of the contrasts. Though these values are unbiased, they are not maximum likelihood estimates and are inappropriate for use with the Akaike information criterion (AIC)~\cite{Akaike1974}. Thus, they were used for analyses involving only the BM model. For comparison with the Ornstein-Uhlenbeck (OU) model, the BM parameters were calculated by maximizing the likelihood. The OU model parameters were also calculated via maximum likelihood estimation. To ensure parameter identfiability and estimate consistency, the root was treated as a random variable~\cite{Ho2013, Ho2014}. Thus, the covariance matrix, $V$, was parameterized as $V_{ij} = e^{\alpha d_{ij}}$ where $d_{ij}$ is the tree distance between tips $i$ and $j$, and $\alpha$ is the selection strength~\cite{Ho2013}.

>>>>

\subsection{Brownian motion and Ornstein-Uhlenbeck analyses}
Brownian motion (BM) model parameters were calculated with two methods. The first used Felsenstein's contrasts algorithm to efficiently calculate roots and contrasts for the disorder scores and features of each region~\cite{Felsenstein1973, Felsenstein1985}. Rates were calculated as the mean of the squares of the contrasts. Though these values are unbiased, they are not maximum likelihood estimates and are inappropriate for use with the Akaike information criterion (AIC)~\cite{Akaike1974}. Thus, they were used for analyses involving only the BM model. For comparison with the Ornstein-Uhlenbeck (OU) model, the BM parameters were calculated by maximizing the likelihood. The OU model parameters were also calculated via maximum likelihood estimation. To ensure parameter identfiability and estimate consistency, the root was treated as a random variable~\cite{Ho2013, Ho2014}. Thus, the covariance matrix, $V$, was parameterized as $V_{ij} = e^{\alpha d_{ij}}$ where $d_{ij}$ is the tree distance between tips $i$ and $j$, and $\alpha$ is the selection strength~\cite{Ho2013}.
